### 2014-06-24 tex/stateDescriptions.tex
took a stab at some text - mainly the abstract and intro

\section{Pseudo-code}
\figref{fig:surface-syntax} defines the surface syntax for the
Javalite language \cite{saints-MS}. The \figref{fig:machine-syntax} is
the machine syntax. The semantics of Javalite is syntax based and
defined as rewrites on a string. The semantics use a CEKS machine
model with a (C)ontrol string representing the expression being
evaluated, an (E)nvironment for local variables, a (K)ontinuation for
what is to be executed next, and a (S)tore for the heap. This paper
only defines salient features of the language and machine relevant to
understanding the new algorithm.

@@

%\item $n$ are numbers, and the set of all positive natural numbers is $\mathbb{N}^+$.
This paper uses a standard definition of constraints $\phi \in \Phi$
assuming all the usual relational operators and connectives. The heap
is a labeled bipartite graph consisting of references $R$ and
locations $L$ in the store. The functions $R$ and $L$ are defined for convenience
in manipulating the labeled bipartite graph.
\begin{itemize}
\item $R(l,f)$ maps location-field pairs from the store to a reference in $R$; and
\item $L(r)$ maps references to a set of location-constraint pairs in the store.
\end{itemize}
A reference is a node that gathers the possible store locations for an
object during symbolic execution. Each store location is guarded by a
constraint that determines the aliasing in the heap. Intuitively, the
reference is a level of indirection between a variable and the store,
and the reference is used to group a set of possible store locations
each predicated on the possible aliasing in the associated constraint.
For a variable (or field) to access any particular store location
associated with its reference, the corresponding constraint must be
satisfied.

\begin{comment}
 defined on value sets $L$ and references
$R$. $R$ and $L$ include the special symbol $\bot$ to indicate an
uninitialized reference and location respectively. Additionally, $L$
includes a special location $\mathtt{NULL}$ for null references.
\end{comment}

Locations are boxes in the graphical representation and indicated with
the letter $l$ in the math. References are circles in the graphical
representation and indicated with the letter $r$ in the math. Edges
from locations are labeled with field names $f \in F$. Edges from the
references are labeled with constraints $\phi \in \Phi$ (we assume
$\Phi$ is a power set over individual constraints and $\phi$ is a set
of constraints for the edge).

@@

% Algorithm2e environment
% http://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
\begin{comment}
\begin{algorithm}
 \SetAlgoLined
 \KwData{this text}
 \KwResult{how to write algorithm with \LaTeX2e }
 initialization\;
 \While{not at end of this document $\wedge x < 2$}{
  read current\;
  \eIf{understand}{
   go to next section\;
   current section becomes this one\;
   }{
   go back to the beginning of current section\;
  }
 }
 \caption{How to write algorithms}
\end{algorithm}
\end{comment}

>>>>

\section{Uber-lazy Operational Semantics}
\label{semantics}

The operational semantics for Uber-lazy
symbolic execution are specified using the Javalite 
language~\cite{saints-MS}. Javalite is an imperative model of Java
that includes many features of the Java language. In this work, we 
present only the salient features of the Javalite
language relevant to understanding the Uber-lazy symbolic execution
algorithm. A detailed explanation of Javalite is available in~\cite{saints-MS}.

Javalite is an imperative model of the Java language
developed to facilitate rapid prototyping 
of model checking algorithms and proofs about the
algorithms. It is specified with a Java-like syntax and a set
of reduction rules for syntacticly executing Javalite programs.
Javalite is based on a variant of the CEKS syntactic 
machine~\cite{Felleisen:1987}. The operational semantics are 
defined using the structure (syntax)
of the language and a set of reduction rules for syntactically
executing Javalite programs. In a CEKS machine, the
(C)ontrol string represents a program, command, or instruction to be
evaluated; it is initialized to a string representing the entire progam. 
An (E)nvironment  maps (local) variables to their values. The (K)ontinuation 
specifies what is to be executed next, and the (S)tore is used to store 
dynamically allocated data, i.e., the heap.

\subsection{Symbolic Store}

At the core of the Uber-lazy symbolic execution algorithm
is a fully symbolic heap, i.e., a heap in which objects
are never materialized as concrete objects during symbolic
execution, but instead are represented using constraints
charactering feasible heap shapes. To represent the heap
store ($S$), our algorithm defines a labeled bi-partite 
graph where $S = (R, L, E)$.  $R$ contains the set of nodes 
representing program \emph{references}.
$L$ contains the set of nodes representing \emph{locations} in the store. 
The store is initialized with two special locations: $null$ and $\bot$ representing a null object
and an uninitialized location respectively. Each edge in the set of labeled
edges, $E$, is uni-directional. An edge from a reference $r \in R$ to a location $l \in L$ is
labeled with a constraint $\phi$ indicating the conditions under which $r$ references
i.e., points to, that location in the store. This paper uses a standard definition
of constraints $\phi \in \Phi$ assuming all of the usual relation operators and connectives.
Reference nodes collect the the
feasible points-to relations for a given program execution path during symbolic execution.
Each edge from a location $l \in L$ to a reference $r \in R$ is labeled with the 
name of a field $f \in F$.

More details here including we assume the input program is typesafe
or if there is a type and a mismatch occurs, then the machine halts.

The machine also halts if an exception is thrown.

\subsection{Syntax}

@@

Javalite programs and expressions are written in a syntax specified by the 
grammar in~\figref{fig:machine-syntax}. The production rules correspond
to the various features supported by Javalite such as classes, fields,
methods, and expressions.

\figref{fig:machine-syntax} specifies
the machine syntax for Javalite. The expression $e$ is equivalent to
a CEKS machine's control string. The

\subsection{Reduction Rules}

We first present the reduction rules

\subsubsection{Basic Reduction Rules}

Most rules presented here - short discussion

\subsubsection{Store Update Rules}

Interesting rules presented here; more elaborate discussion

Start off with helper functions for rules that manipulate the store...

@@
